Xor-Some Preregistered Study: Analyses

### 2021-10-31 analysis/main/01_xor-some_prereg_preprocessing_final.Rmd
add final N200 analysis

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N233_anonym.csv")

@@

cat(" Number of participants failing attention checks: ", d_native_attention_failed %>% distinct(submission_id) %>% count() %>% pull() )
```

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_N233_test.csv")
```

@@

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_N233_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_N233_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_N233_zScored_wide.csv")
```

>>>>

First, the data is loaded.
```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N275_anonym.csv")

@@

cat(" Number of participants failing attention checks: ", d_native_attention_failed %>% distinct(submission_id) %>% count() %>% pull() )

#d_attention_fail_IDs <- right_join(d_raw, d_native_attention_failed, by = c("submission_id")) %>% select(submission_id, prolific_id) %>% distinct()
#d_attention_fail_IDs %>% write_csv("~/Documents/Research/XOR/raw_data/xor-some_prereg_failed_attention_prolificIDs_final.csv")
```

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_final_test.csv")
```

@@

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```
Exclude the 201st participant for target N=200:
```{r, results='hide'}
d_full_clean %>% arrange(., desc(submission_id)) %>% distinct() %>% pull(submission_id)

# exclude participant with last submission_id
d_full_clean <- d_full_clean %>% filter(submission_id != 2620)

cat(" Nr. of participants left after cleaning and N=200 extraction: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_final_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
```

### 2021-10-31 analysis/main/02_xor-some_prereg_plots_final.Rmd
add final N200 analysis

Read data created in preprocessing script:
```{r}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_N18_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_N18_zScored_long.csv")
d_test_raw <- read_csv("./../../data/main/results_prereg_raw_N18_test.csv")
```

>>>>

Read data created in preprocessing script:
```{r}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_test <- read_csv("./../../data/main/results_prereg_raw_final_test.csv")
```

### 2021-10-31 analysis/main/03_xor-some_prereg_analysis_final.Rmd
add final N200 analysis

Read data created in preprocessing script:
```{r}
d_critical_zScored_wide <- read_csv("./../../data/results_prereg_tidy_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/results_prereg_tidy_zScored_long.csv")
```

@@

model_SI <- brm(target ~ prior*competence*relevance* main_type +
                  # (1 + prior + competence + relevance + main_type || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

@@

Model with binary predictors:
```{r}
d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered, prior_class, class_condition) %>% 
  unique() %>% 
  pivot_wider(
    names_from = class_condition, 
    values_from = prior_class
  )  %>%
  mutate(relevance = factor(relevance, levels = c(1, 0)),
         competence = factor(competence, levels = c(1, 0)),
         prior = factor(prior, levels = c(1, 0)),
         main_type = as.factor(main_type)) %>% 
  filter(block_extended == "target") -> d_critical_wide_cat_zScored
# sum code predictors
# low prior: -1, high prior:: 1 
contrasts(d_critical_wide_cat_zScored$prior) <- contr.sum(2)
# low comp : -1, high comp : 1
contrasts(d_critical_wide_cat_zScored$competence) <- contr.sum(2)
# low rel: -1, high rel: 1
contrasts(d_critical_wide_cat_zScored$relevance) <- contr.sum(2)
# leave main type dummy coded
contrasts(d_critical_wide_cat_zScored$main_type)

@@

```
```{r}
summary(model_xor_cat_zScored)
```

Model with aggregated by-story ratings:
```{r, results='hide'}
d_critical_zScored_wide_byItem <- d_critical_zScored_wide %>% ungroup() %>%
  group_by(title, main_type) %>%
  summarize(mean_response = mean(target),
            mean_prior = mean(prior),
            mean_relevance = mean(relevance),
            mean_competence = mean(competence))

@@

>>>>

Read data created in preprocessing script:
```{r}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
```

@@

model_SI <- brm(target ~ prior*competence*relevance* main_type +
                   (1 + prior + competence + relevance + main_type || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

@@

Model with binary predictors:
```{r, results='hide', message=FALSE, warning=FALSE}
d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered, prior_class, class_condition) %>% 
  unique() %>% 
  pivot_wider(
    names_from = class_condition, 
    values_from = prior_class
  )  %>%
  mutate(relevance = factor(relevance, levels = c(1, 0)),
         competence = factor(competence, levels = c(1, 0)),
         prior = factor(prior, levels = c(1, 0)),
         main_type = as.factor(main_type)) %>% 
  filter(block_extended == "target") -> d_critical_wide_cat_zScored
# sum code predictors
# low prior: -1, high prior:: 1 
contrasts(d_critical_wide_cat_zScored$prior) <- contr.sum(2)
# low comp : -1, high comp : 1
contrasts(d_critical_wide_cat_zScored$competence) <- contr.sum(2)
# low rel: -1, high rel: 1
contrasts(d_critical_wide_cat_zScored$relevance) <- contr.sum(2)
# leave main type dummy coded
contrasts(d_critical_wide_cat_zScored$main_type)

@@

```
```{r}
summary(model_xor_cat_zScored)
```
Now extract posterior contrasts of interest from categorical model: effects of each predictor \{prior, competence and relevance\} for each trigger.

```{r}
model_xor_cat_zScored %>% spread_draws(b_Intercept, b_prior1, b_competence1, b_relevance1,
                          b_main_typexor, `b_prior1:competence1`,
                          `b_prior1:relevance1`, `b_competence1:relevance1`,
                          `b_prior1:main_typexor`, `b_competence1:main_typexor`,
                          `b_relevance1:main_typexor`, `b_prior1:competence1:relevance1`, 
                          `b_prior1:competence1:main_typexor`, `b_prior1:relevance1:main_typexor`,
                          `b_competence1:relevance1:main_typexor`, 
                          `b_prior1:competence1:relevance1:main_typexor`) %>% 
  mutate(
    prior_xor = 2 * b_prior1 + 2* `b_prior1:main_typexor`,
    prior_some = 2 * b_prior1,
    competence_xor = 2 * b_competence1 + 2* `b_competence1:main_typexor`,
    competence_some = 2 * b_competence1,
    relevance_xor =  2 * b_relevance1 + 2* `b_relevance1:main_typexor`,
    relevance_some = 2* b_relevance1
  ) -> model_xor_cat_zScored_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_cat <- model_xor_cat_zScored_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_cat
```
```{r}
test_conjunction_of_all_hypotheses(posterior_hypotheses_cat)
```

Model with aggregated by-story ratings:
```{r, results='hide', message=FALSE, warning=FALSE}
d_critical_zScored_wide_byItem <- d_critical_zScored_wide %>% ungroup() %>%
  group_by(title, main_type) %>%
  summarize(mean_response = mean(target),
            mean_prior = mean(prior),
            mean_relevance = mean(relevance),
            mean_competence = mean(competence))

@@

Extract posterior contrasts of interest from by-story mean based model: effects of each predictor \{prior, competence and relevance\} for each trigger.

```{r}
model_means %>% spread_draws(b_Intercept, b_mean_prior, b_mean_competence, b_mean_relevance,
                          b_main_typexor) %>% 
  mutate(
    prior_xor = b_mean_prior,
    prior_some = b_mean_prior,
    competence_xor = b_mean_competence,
    competence_some = b_mean_competence,
    relevance_xor =  b_mean_relevance,
    relevance_some = b_mean_relevance
  ) -> model_means_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_means <- model_means_posteriors %>% 
  select(prior_xor, prior_some, 
         competence_xor, competence_some,
         relevance_xor, relevance_some) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_means
```

```{r}
test_conjunction_of_all_hypotheses(posterior_hypotheses_means)
```
